### 2019-08-30 reports/paper1/paper.tex
Change github address
align defect detect figures

\section{Appendix}
Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanip/oxwasp_insideout}.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted white positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

>>>>

\section{Appendix}
Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanlo77/oxwasp_insideout}.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=5.0cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted white positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

### 2019-08-30 reports/thesis/chapters/5_inference.tex
align defect detect figures

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}
